European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-22 manuscript/manuscript.qmd
Add results (rough) (#24)
* Interpret pro-EUP results

* interpret conditions and link to neoliberalism

>>>>

The only favourable treatment associated with American influence, perhaps surprisingly, is a reduction in the number of IMF conditions. In contrast, ties with Europe are not associated with such benefits. This finding echoes the argument by @lutz2014, who suggest that European actors have historically adhered more strictly to economic orthodoxy—most visibly during the Eurozone crisis—despite such policies traditionally being associated with the United States under the so-called “Washington Consensus.” Although the European adoption of neoliberal economic doctrines became especially prominent after the crisis, it is notable that similar patterns are already evident in the pre-2010 data examined here.
